Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 algorithm_general.tex
stating once that proofs are in appendix

We begin by bounding the length of any phase, which will support bounding
the regret of early rounds
(before tail bounds have kicked in). We prove Lemma~\ref{lem:phase-length} in Appendix~\ref{sec:lemma4-proof}.

@@

We leave the proof of Lemma~\ref{lem:round-prob} in the Appendix~\ref{sec:lemma5-proof}. Next, we show the complementary part:
when \AccEU{t}{x} happens, no myopic agent incurs large regret. We prove Lemma~\ref{lem:right-choice} in the Appendix~\ref{sec:lemma7-proof}.

>>>>

We begin by bounding the length of any phase, which will support bounding
the regret of early rounds
(before tail bounds have kicked in). The proof of Lemma~\ref{lem:phase-length} and all other proofs missing in the main paper may be found in the Appendix.

@@

Next, we show the complementary part:
when \AccEU{t}{x} happens, no myopic agent incurs large regret.
